---
output: github_document
---

#Changing Data to work for iNext Package

```{r}
library(ggplot2)
library(tidyverse)
library(reshape2)
library(lubridate)
library(viridis)
library(data.table)
library(forcats)
library(iNEXT)
library(RColorBrewer)
```


```{r}


invert_all <- read_csv("countnormalizedeelgrasscompileddatechange.csv")

#converts date to good format 
invert_all$date <- as.Date(invert_all$date, format = "%d-%h-%y")

invert_all$date<-format(invert_all$date, format="%m-%d")

#filter out all completed 
invert_all_comp <- invert_all %>%
     filter(comp == 1)

#rewrites Habitat as numeric
invert_all_comp$eel <- as.numeric(invert_all_comp$eel)

#changes habitat from numeric to character                            
invert_all_comp <- invert_all_comp %>% 
  mutate(eel = ifelse(eel == 1, "Eel", eel))
invert_all_comp <- invert_all_comp %>% 
  mutate(eel = ifelse(eel == 0, "NonEel", eel))



#Renames Eel 
invert_all_comp <- rename(invert_all_comp, Habitat = eel)

```


Want list of Sites and then want to get them horizontal. Like I already have for Brian.... Check baby... Including dates, yes but we are going to sum for dates for region and habitat. Yes. 

Want to have column headings as assemblages, Individual‐based abundance data (datatype="abundance"): Input data for each assemblage/site include samples species abundances in an empirical sample of n individuals (“reference sample”). When there are N assemblages, input data consist of an S by N abundance matrix, or N lists of species abundances.


```{r results = 'asis'}
#Need to sum up species counts for each habitat.
invert_all_comp <- summarise(group_by(invert_all_comp, region, Habitat, orgnsm), sumcount =sum(act_count))

#Put habitat and regions together
invert_all_comp <- invert_all_comp %>% 
  unite("Site", region, Habitat, sep = "_")

#dataframe so species IDs are now in rows and Habitat in columns
hab_cols <- invert_all_comp %>% 
  spread(Site, sumcount)



orgnsm_cols <- invert_all_comp %>% 
  spread(orgnsm, sumcount)

#set species names to row names in hab_cols 

hab_col_rem <- (hab_cols[,c(-1)])
round(hab_col_rem,0)
class(hab_col_rem)

hab_col_rem[is.na(hab_col_rem)] <- 0


hab_col_rem_list <- as.list(hab_col_rem)

bedwell <- as.list(hab_col_rem[,1:2])
fraser <- as.list(hab_col_rem[,3:4])
qual <- as.list(hab_col_rem[,7:8])
koeye <- as.list(hab_col_rem[,5:6])
tahsis <- as.list(hab_col_rem[,9:10])

iNEXT(hab_col_rem_list, q=2, datatype="abundance")


bed <- iNEXT(bedwell, q=c(0),  datatype="abundance",nboot = 100)
ggiNEXT(bed, type=1, color.var = "site") +  theme_bw(base_size=18) + theme(legend.position="bottom", legend.title=element_blank())
ggsave("sr_bed.png")
fra <- iNEXT(fraser, q=0,  datatype="abundance",nboot = 100)
ggiNEXT(fra, type=1, color.var = "site") +  theme_bw(base_size=18) + theme(legend.position="bottom", legend.title=element_blank()) 
ggsave("sr_fraser.png")
qua <- iNEXT(qual, q=0,  datatype="abundance",nboot = 100)
ggiNEXT(qua, type=1, color.var = "site") +  theme_bw(base_size=18) + theme(legend.position="bottom", legend.title=element_blank())
ggsave("sr_qual.png")
koe <- iNEXT(koeye, q=0,  datatype="abundance",nboot = 100)
ggiNEXT(koe, type=1, color.var = "site") +  theme_bw(base_size=18) + theme(legend.position="bottom", legend.title=element_blank())
ggsave("sr_koeye.png")
tah <- iNEXT(tahsis, q=0,  datatype="abundance",nboot = 100)
ggiNEXT(tah, type=1, color.var = "site") +  theme_bw(base_size=18) + theme(legend.position="bottom", legend.title=element_blank())
ggsave("sr_tahsis.png")





#final product is matrix of species counts aggregated by habitat

#class(adj_qual2)<-"numeric"

#Reg.rar<-iNEXT(adj_qual2,q=0,datatype = "abundance",nboot=1000)
#ggiNEXT(Reg.rar) + theme_bw()

```


```{r}

invert_all_comp %>% 
sweep(invert_all_comp, 1, rowSums(invert_all_comp), '/')
```



```{r}

```

