---
title: "MNO_Eelgrass"
author: "Matt Madsen"
date: "December 17, 2016"
output: github_document
---

#This differs from last analysis by removing any samples with less than 200 individuals counted 

#Next steps 

1. Add in the highest relative abundances into each table 

2. Clean up plots so they are in line 

3. NMDS Plot 

4. Box Boxplots for each one, reorder by mean 

5. Cluster Analysis

6. Biomass entry as weighting factors. - Take abundance then times by biomass, then take relative biomass. 

```{r}
library(ggplot2)
library(tidyverse)
library(reshape2)
library(lubridate)
library(viridis)
library(data.table)
library(forcats)
library(RColorBrewer)
library(forestplot)
```

#Load all Data, pull out information we want. 
```{r}
invert_all <- read_csv("CountNormalizedEelgrassCompiledDateChange.csv")
invert_all <- invert_all %>% 
  filter(Sum >200)
invert_all$date <- as.Date(invert_all$date, format = "%d-%h-%y")
invert_all_comp <- invert_all %>%
     filter(comp == 1)

invert_all_comp$eel <- as.numeric(invert_all_comp$eel)

invert_all_comp <- invert_all_comp %>% 
  mutate(rel_abun_per = rel_abun*100) 

#change Eelgrass

invert_all_comp <- invert_all_comp %>% 
  mutate(eel = ifelse(eel == 1, "Eel", eel))
invert_all_comp <- invert_all_comp %>% 
  mutate(eel = ifelse(eel == 0, "No_Eel", eel))

#join sz and orgnsm
invert_all_comp <- invert_all_comp %>% 
  unite("sz_orgnsm", sz_frac, orgnsm, sep = "_")

#Renames Column from Eel to Habitat
invert_all_comp <- rename(invert_all_comp, habitat = eel)

invert_all_digested <- invert_all_comp %>% 
  select(region, date, set, habitat, Paired, sz_orgnsm, count, rel_abun, rel_abun_per)


write_csv(invert_all_digested, "eelgrass_digested_over200.csv")
```



#Summarize Data for mean, n and total across the regions for each respective individual and habitat.

```{r}
SE <- function(x) sd(x)/sqrt(length(x))

(invert_mean <- invert_all_digested %>% 
  select(region, habitat, rel_abun_per, sz_orgnsm, count) %>% 
   group_by(region, sz_orgnsm, habitat) %>% 
   summarise(mean_abun_per = mean(rel_abun_per), SE = SE(rel_abun_per), n= n_distinct(rel_abun_per), total= sum(count)))

```

#Make all NA turn into 0 
```{r}
invert_mean[is.na(invert_mean)] <- 0
```
#Spread Data Out for Eelgrass and Non Eelgrass
```{r}
#set up in nice table to ensure doing right thing
  spread_mean <- invert_mean %>% 
  select(region, habitat, mean_abun_per, sz_orgnsm) %>% 
  spread(habitat,mean_abun_per)

spread_mean[is.na(spread_mean)] <- 0

  spread_SE <- invert_mean %>% 
  select(region, habitat, SE, sz_orgnsm) %>% 
  spread(habitat,SE) 
  
spread_SE[is.na(spread_SE)] <- 0

  spread_n <- invert_mean %>% 
  select(region, habitat, n, sz_orgnsm) %>% 
  spread(habitat,n)
  
spread_n[is.na(spread_n)] <- 0
```



#Take the difference between Eel and Non Eel, add the n and add the SE. 
```{r}
  (spread_mean <- spread_mean %>% 
  mutate(Hab_diff = Eel - No_Eel) %>% 
  select(region, sz_orgnsm, Hab_diff))
  
  (spread_SE <- spread_SE %>% 
  mutate(SE_Total = Eel + No_Eel) %>% 
  select(region, sz_orgnsm, SE_Total))

  (spread_ntot <- spread_n %>% 
    mutate(n_total= Eel + No_Eel) %>% 
  select(region, sz_orgnsm, n_total))

  (joined <- full_join(spread_mean,spread_SE))
 
joined <- joined %>% 
mutate(upper = Hab_diff + 1.96*SE_Total, lower = Hab_diff - 1.96*SE_Total) %>% 
  select(Hab_diff, upper, lower)
```


#Fraser, need to write this into a function

##Now need to split here, is there a better way to do this? Need to figure out. 


##Picking Region and Padding out 
```{r}
#filters out Fraser 
joined_fraser <-  joined %>% filter(region == "Fraser")

#Made larger DataFrame to Pad Dada
pad <- (data_frame(region= c("Fraser", "Fraser"), Hab_diff= c(NA, NA)))

#Padded joined with Fraser
padded <- full_join(pad, joined_fraser)
```

##Working to put into proper data table format for text input 
```{r}
spread_fraser <- spread_n %>% filter(region == "Fraser")

new <- spread_fraser[,c(2,3,4)]

middle <- c("", "(n)", "(n)")

new1 <- rbind(middle, new)

top <- c("SizeFraction_Organism","Eelgrass", "Non-Eelgrass")

frasertext <- rbind(top,new1)
```


##Fraser Plot 
```{r}

png("forestfraser200.png", width=8, height=11, units="in", res=300)
forestfraser <- forestplot(frasertext, padded$Hab_diff, padded$lower, padded$upper,
                           zero= 0, 
                           txt_gp= fpTxtGp(cex= 1, xlab = gpar(cex=0.7), 
                           ticks = gpar(cex=0.75)), 
                           col=fpColors(box="royalblue",line="darkblue"), 
                           lineheight = "auto",
                           title = "Fraser with >200 ind.", 
                           xlab= "Diff. in R.A. of Eel. vs. Non Eel. (Mean % ± 95% C.I.)", 
                           boxsize = 0.2, 
                           hrzl_lines = list("3" = gpar(col="#444444")), 
                           is.summary=c(TRUE,TRUE,rep(FALSE,30)))

dev.off()
```

#Tahsis, spot the function 

```{r}
#need to into function (x) { all of this stuff, how to return certain parts in a function???, more reading}
joined_tahsis<-  joined %>% filter(region == "Tahsis") #put in x

#Made larger DataFrame to Pad Dada
pad <- (data_frame(region= c("tahsis", "tahsis"), Hab_diff= c(NA, NA))) #put in x 

#Padded joined with Fraser
padded <- full_join(pad, joined_tahsis)
```


```{r}
#spread it out
spread_tahsis <- spread_n %>% filter(region == "Tahsis")

#pulled out needed data, won't break otherwise
new <- spread_tahsis[,c(2,3,4)]

#middle 
middle <- c("", "(n)", "(n)")

#make new 
new1 <- rbind(middle, new)

#add last piece to top
top <- c("SizeFraction_Organism","Eelgrass", "Non-Eelgrass")

#assemble text 
tahsistext <- rbind(top,new1)
```


```{r}
png("foresttahsis200.png", width=8, height=11, units="in", res=300)

foresttahsis <- forestplot(tahsistext, padded$Hab_diff, padded$lower, padded$upper,
                           zero= 0, 
                           txt_gp= fpTxtGp(cex= 1, xlab = gpar(cex=0.70), ticks = gpar(cex=0.75)), 
                           col=fpColors(box="royalblue",line="darkblue"), 
                           lineheight = "auto",
                           title = "tahsis > 200 ind.",
                           xlab= "Diff. in R.A. of Eel. vs. Non Eel. (Mean % ± 95% C.I.)",
                           boxsize = 0.2,
                           hrzl_lines = list("3" = gpar(col="#444444")), 
                           is.summary=c(TRUE,TRUE,rep(FALSE,(length(padded$Hab_diff)-2))))
  dev.off()
```

#Qualicum 
```{r}
#need to into function (x) { all of this stuff, how to return certain parts in a function???, more reading}
joined_Qualicum<-  joined %>% filter(region == "Qualicum") #put in x

#Made larger DataFrame to Pad Dada
pad <- (data_frame(region= c("Qualicum", "Qualicum"), Hab_diff= c(NA, NA))) #put in x 

#Padded joined with Fraser
padded <- full_join(pad, joined_Qualicum)
```


```{r}
#spread it out
spread_Qualicum <- spread_n %>% filter(region == "Qualicum")

#pulled out needed data, won't break otherwise
new <- spread_Qualicum[,c(2,3,4)]

#middle 
middle <- c("", "(n)", "(n)")

#make new 
new1 <- rbind(middle, new)

#add last piece to top
top <- c("SizeFraction_Organism","Eel", "Non-Eel")

#assemble text 
Qualicumtext <- rbind(top,new1)
```


```{r}
png("forestqualicum200.png", width= 15 , height=20, units="in", res=300)

forestQualicum <- forestplot(Qualicumtext, padded$Hab_diff, padded$lower, padded$upper,
                           zero= 0, 
                           txt_gp= fpTxtGp(cex= 1.5, xlab = gpar(cex=2), ticks = gpar(cex=1.5)), 
                           col=fpColors(box="royalblue",line="darkblue"), 
                           lineheight = "auto",
                           title = "Qualicum > 200 ind.",
                           xlab= "Diff. in R.A. of Eel. vs. Non Eel. (Mean % ± 95% C.I.)",
                           boxsize = 0.3,
                           hrzl_lines = list("3" = gpar(col="#444444")), 
                           is.summary=c(TRUE,TRUE,rep(FALSE,(length(padded$Hab_diff)-2))))
  dev.off()
```



#Koeye 
```{r}
#need to into function (x) { all of this stuff, how to return certain parts in a function???, more reading}
joined_koeye<-  joined %>% filter(region == "Koeye") #put in x

#Made larger DataFrame to Pad Dada
pad <- (data_frame(region= c("Koeye", "Koeye"), Hab_diff= c(NA, NA))) #put in x 

#Padded joined with Fraser
padded <- full_join(pad, joined_koeye)

```


```{r}
#spread it out
spread_koeye <- spread_n %>% filter(region == "Koeye")

#pulled out needed data, won't break otherwise
new <- spread_koeye[,c(2,3,4)]

#middle 
middle <- c("", "(n)", "(n)")

#make new 
new1 <- rbind(middle, new)

#add last piece to top
top <- c("SizeFraction_Organism","Eel", "Non-Eel")

#assemble text 
koeyetext <- rbind(top,new1)
```


```{r}
png("forestkoeye200.png", width= 8 , height=11, units="in", res=300)

forestkoeye <- forestplot(koeyetext, padded$Hab_diff, padded$lower, padded$upper,
                           zero= 0, 
                           txt_gp= fpTxtGp(cex= 1, xlab = gpar(cex=0.7), ticks = gpar(cex=0.75)), 
                           col=fpColors(box="royalblue",line="darkblue"), 
                           lineheight = "auto",
                           title = "Koeye >200 ind.",
                           xlab= "Diff. in R.A. of Eel. vs. Non Eel. (Mean % ± 95% C.I.)",
                           boxsize = 0.2,
                           hrzl_lines = list("3" = gpar(col="#444444")), 
                           is.summary=c(TRUE,TRUE,rep(FALSE,(length(padded$Hab_diff)-2))))
  dev.off()
  
  (forestkoeye)
```
#Bedwell 

```{r}
#need to into function (x) { all of this stuff, how to return certain parts in a function???, more reading}
joined_bedwell<-  joined %>% filter(region == "Bedwell") #put in x

#Made larger DataFrame to Pad Dada
pad <- (data_frame(region= c("Bedwell", "Bedwell"), Hab_diff= c(NA, NA))) #put in x 

#Padded joined with Fraser
padded <- full_join(pad, joined_bedwell)

```


```{r}
#spread it out
spread_bedwell <- spread_n %>% filter(region == "Bedwell")

#pulled out needed data, won't break otherwise
new <- spread_bedwell[,c(2,3,4)]

#middle 
middle <- c("", "(n)", "(n)")

#make new 
new1 <- rbind(middle, new)

#add last piece to top
top <- c("SizeFraction_Organism","Eel", "Non-Eel")

#assemble text 
bedwelltext <- rbind(top,new1)
```


```{r}
png("forestbedwell200.png", width= 8 , height=11, units="in", res=300)

forestbedwell <- forestplot(bedwelltext, padded$Hab_diff, padded$lower, padded$upper,
                           zero= 0, 
                           txt_gp= fpTxtGp(cex= 1, xlab = gpar(cex=0.9), ticks = gpar(cex=0.75)), 
                           col=fpColors(box="royalblue",line="darkblue"), 
                           lineheight = "auto",
                           title = "Bedwell > 200 ind.",
                           xlab= "Diff. in R.A. of Eel. vs. Non Eel. (Mean % ± 95% C.I.)",
                           boxsize = 0.2,
                           hrzl_lines = list("3" = gpar(col="#444444")), 
                           is.summary=c(TRUE,TRUE,rep(FALSE,(length(padded$Hab_diff)-2))))
  dev.off()
  

```
